---
title: "Understanding Google Play Application Reviews"
author: "RTime2Shine"
date: "12/7/19"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-packages, warning = FALSE, message=FALSE}
library(tidyverse)
library(broom)
library(knitr) 
library(skimr)
library(readr)
library(ggplot2)
library(stringr)
library(lubridate)
library(Sleuth3) 
library(ISLR)
library(leaps)
library(dplyr)
library(rms)
```

```{r load-data, warning = FALSE, message=FALSE}
apps <- read_csv("/cloud/project/02-data/googleplaystore.csv")
levels(apps$`Content Rating`) <- c("Adults Only","Everyone","Mature", "Teen", "Unrated")
apps <- filter(apps, Reviews <= 203579)
apps$`Rating` <- as.numeric(apps$`Rating`)
apps <- apps %>%
  na.omit(apps)
```

```{r fact recode, warning = FALSE, message = FALSE}
apps <- apps %>%
  mutate(Category = as.factor(Category)) %>%
  mutate(Size = as.factor(Size)) %>%
  mutate(Installs = as.factor(Installs)) %>%
  mutate(Type = as.factor(Type)) %>%
  mutate(`Content Rating` = as.factor(`Content Rating`)) %>%
  mutate(Genres = as.factor(Genres)) %>%
  mutate(Category = as.factor(Category))

apps$Price <- str_replace(apps$Price, "\\$", "")
apps$Size <- str_replace(apps$Size, "\\M", "")
apps$Installs <- str_replace(apps$Installs, "\\+", "")
apps$`Content Rating`<- str_replace(apps$`Content Rating`, "\\+", "")
apps$`Content Rating`<- str_replace(apps$`Content Rating`, "[[:digit:]]+", "")
apps$Price <- as.numeric(gsub('[$.]', '', apps$Price))
apps$`Android Ver`<-gsub("\\..*","",apps$`Android Ver`)
apps$`Android Ver`<-as.factor(apps$`Android Ver`)
apps$`Android Ver`[apps$`Android Ver` == "NaN"] <- NA
```

```{r dates, warning = FALSE, message = FALSE}
apps <- apps %>%
  mutate(date_new = mdy(`Last Updated`))
apps <- apps %>%
  mutate(date_since = mdy("August 8, 2018") - date_new)
```

```{r price-relevel, warning = FALSE, message = FALSE}
apps <- apps %>%
  mutate(Price = case_when(Price == 0 ~ "Free", Price < 500 & Price > 0 ~ "Between $0 and $4.99", Price > 500 ~ "Greater than $5"))

apps <- apps %>%
  mutate(Price = fct_relevel(Price, "Free", "Between $0 and $4.99", "Greater than $5"))
```

```{r installs-relevel, warning = FALSE, message = FALSE}
apps$`Installs`<- as.numeric(gsub(",", "", apps$`Installs`))

apps <- apps %>%
  mutate(Installs = case_when(Installs < 100 ~ "Less than 100", Installs < 1000 & Installs >= 100 ~ "Between 100 and 1,000", Installs < 10000 & Installs >= 1000 ~ "Between 1,000 and 10,000", Installs < 100000 & Installs >= 10000 ~ "Between 10,000 and 100,000", Installs >= 100000 ~ "100,000 or Greater"))


apps <- apps %>%
  mutate(Installs = fct_relevel(Installs, "Less than 100", "Between 100 and 1,000", "Between 1,000 and 10,000", "Between 10,000 and 100,000", "100,000 or Greater"))

skim(apps, Installs)
```

```{r sizerelevel, warning = FALSE, message = FALSE}
apps$`Size`<- sub('k$', '', apps$`Size`)
apps$`Size`<- as.numeric(gsub("Varies with device", 0.001 , apps$`Size`))
apps <- apps %>%
  mutate(Size = case_when(Size == 0.001 ~ "Varies with device", Size < 100 ~ "Less than 100 MB", Size > 100 ~ "Greater than 100 MB"))

```

```{r rating-distribution, warning = FALSE, message = FALSE}
ggplot(data = apps, aes(x = Rating)) + 
  geom_histogram(binwidth = 0.1, fill = "blue") + 
  xlim(0,5) + labs(title = "Distribution of App Ratings")
```


```{r log reviews, warning = FALSE, message = FALSE}
apps <- apps %>% 
  mutate(log_reviews = log(Reviews)) 
ggplot(apps, aes(x = log_reviews)) + geom_histogram(binwidth = 0.5)
apps %>%
  summarise(median(log_reviews), max(log_reviews), IQR(log_reviews))
```

```{r category pop, warning = FALSE, message = FALSE}
apps %>%
  count(Category) %>%
  arrange(-n) %>%
  mutate(freq = n/sum(n))
```

```{r relevel cat, warning = FALSE, message = FALSE}
apps <- apps %>%
  mutate(category_simp = case_when( 
    apps$Category %in% c("FAMILY","GAME", "TOOLS","MEDICAL", "LIFESTYLE", "FINANCE") ~ "Top 6 Categories", 
    TRUE ~ "Others"))

apps %>%
  count(Category, category_simp) %>%
  arrange(desc(n))
```

```{r relevel andriod ver}
apps %>%
  count(`Android Ver`) %>%
  arrange(desc(n))

apps <- apps %>%
  na.omit(`Android Ver`) %>%
  mutate(androidver_simp = case_when( 
    `Android Ver` %in% c(1,2,3,4) ~ "1-4", 
    `Android Ver` %in% c(5,6,7,8) ~ "5-8",
    TRUE ~ "Varies with Device"))

apps %>%
  count(`Android Ver`, androidver_simp) %>%
  arrange(desc(n))
```

```{r}
apps <- apps %>%
  mutate(content_simp = case_when( 
    `Content Rating` == "Everyone" ~ "Everyone",
    `Content Rating` == "Teen" ~ "Teen",
    `Content Rating` == "Mature" ~ "Mature",
    `Content Rating` == "Everyone" ~ "Everyone",
    `Content Rating` == "Adults only" ~ "Adults only",
    `Content Rating` == "Unrated" ~ "Unrated"))
apps %>%
  count(`Content Rating`, content_simp) %>%
  arrange(desc(n))
```


# Model Selection

```{r full-model}
apps <- apps %>%
  na.omit(apps)
full_model <- lm(Rating ~ category_simp + log_reviews + Size + Installs + Price + `Content Rating` + androidver_simp + date_since, data = apps)
kable(tidy(full_model),format="html",digits=4)
```

```{r vif}
tidy(vif(full_model))
```


```{r bic-back}
regfit_backward <- regsubsets(Rating ~ category_simp + log_reviews + Size + Installs + Price + `Content Rating` + androidver_simp + date_since, data = apps, method="backward")
sel_summary <- summary(regfit_backward)
coef(regfit_backward, which.min(sel_summary$bic))
```

```{r bic-forward}
regfit_forward <- regsubsets(Rating ~ category_simp + log_reviews + Size + Installs + Price + `Content Rating` + androidver_simp + date_since, data = apps, method="forward")
sel_summary <- summary(regfit_forward)
coef(regfit_forward, which.min(sel_summary$bic))
```



## Section 1: Introduction (includes introduction and exploratory data analysis)
### Motivaton
As technology has become increasingly prevalent around the world, there has been a change in the consumption of media. One of these ways is via the purchase of applications (apps) for various smartphones and other devices. Several technology companies, including Apple and Google, run virtual stores for these apps in which a person can download an app for their device. These apps can be for various purposes like socializing, playing games, or watching television and movies, among others. While any user of a phone can agree that apps hold an important effect on how one interacts with technology on a daily basis, the weight of the impact becomes even more shocking when one looks at the figures- in 2018, global app downloads topped 194 billion (Dignan).

Our motivation for this project is to understand what makes apps (from the Google Play store specifically) have favorable ratings. Understanding the ratings of an app is important for several reasons. First, ratings can be important to the provider- in this case Google- who can decide whether an app should continue to be sold to maintain their quality standards. Ratings are additionally useful as a direct line of communication between the user and the developers- often, developers are made aware of changes that need to be made to their apps through user feedback. Lastly, reviews serve to inform potential users of an app whether or not it is worth their time and can affect future downloads. Considering that app users are predicted to spend about $120 billion in app stores in 2019, understanding which apps do well on the Play Store and what factors affect app performance is an immensely important question to gain more insight into. 

### Research Question & Hypothesis
This leads us to introduce our main research question: What are the relevant factors that affect the rating given for apps in the Google Play store? Although this project will give a detailed attempt to answer this question, our preliminary hypothesis is that the variables Category, Price, Installs, and Content Rating are the predictor variables that will most affect a given app rating and popularity, as measured by the number of installs of the app. We believe that these variables are indicative of an apps useability and likeness (as determined by variables like content rating and categories in how people may be drawn to an app) as well as its accessibility (price). Furthermore, once we test our hypothesis and determine which factors are relevant, we will attempt to use that information to predict the success of an app as measured by its rating.

### The Data

The dataset was obtained from Kaggle. According to Kaggle, the dataset was scraped directly from the Google Play Store in August 2018. Each observation represents one individual app on the Google Play Store. This particular dataset has 13 variables with 9660 observations. The variables consist of various information collected about each application (which represents a row) in the dataset. This information includes the apps category in the app store, its average rating, price, content rating, the number of installs, among other metrics. In our Exploratory Data Analysis, we will further explain the use of each of these variables and determine which of these may be significant for and relevant in our analysis. The response variable in our investigation is `Rating` which is the mean rating out of 5.0 for an application in the Google Play Store. This is a numeric variable. 

### Exploratory Data Analysis
#### Data Wrangling

#### Univariate Analysis

#### Bivariate Analysis

#### Possible Interactions

## Section 2: Regression Analysis (includes the final model and discussion of assumptions)

### Model Process
### Model Selection
### Interactions & Our Updated Model
### Assumptions
### Model Assesment
### Model Interpretation

## Section 3: Discussion and Limitations 

## Section 4: Conclusion

## Section 5: Additional Work

### References

Gupta, Lavanya. Kaggle. Jan. 2019, www.kaggle.com/lava18/google-play-store-apps?fbclid=IwAR36EMS2jg5fhPi-BQlX6Mv4MCk8YUm2XmyOLt0zsKkNyc9JK-JD7aLy-6I. Accessed 30 Oct. 2019. 

Dignan, Larry. “App Economy Expected to Be $120 Billion in 2019 as Small Screen Leads Digital Transformation Efforts.” ZDNet, ZDNet, 16 Jan. 2019, www.zdnet.com/article/app-economy-expected-to-be-120-billion-in-2019-as-small-screen-leads-digital-transformation-efforts/
