---
title: "PROJECT TITLE"
subtitle: "Project Proposal"
author: "RTime2Shine"
date: "October 29, 2019"
output: github_document
---

## Section 1. Introduction

## Section 2. Analysis plan


```{r load-packages}
library(tidyverse)
library(broom)
library(knitr) 
library(ggplot2)
```
```{r load-data}
apps <- read_csv("/cloud/project/02-data/googleplaystore.csv")
```

## Section 3. Regression Analysis Plan

### Possible Interactions
Since our question of interest is measuring the effect of various qualities of an app on its rating, there are a number of interactions within our predictor variables to consider. First, there is a possible interaction between content rating and genres. 

```{r int-content}
ggplot(apps, aes(x = Genres, y = Rating, color = `Content Rating`)) + geom_point() +
labs( title = "Relationship between Genre and Rating", x ="Genre ", y = "Rating out of 5")
```

As shown in the plot above, there may be a correlation between having a lower content rating and being in a “family-friendly” genre such as Family or game. This interaction will have to be considered when building the model. Secondly, there may be an interaction between number of reviews and installs. 

```{r int-installs}
ggplot(apps, aes(x = Reviews, y = Rating, color = Installs)) + geom_point() +
labs( title = "Relationship between Reviews and Rating", x ="# of Reviews ", y = "Rating out of 5")
```

As shown in this plot, as the number of reviews for an app increases, so does the number of installs. This is indicative of an app being popular so there is most likely some interaction between these two variables in the dataset. Thirdly, there may be an interaction between Type and Price. Since Type is an indicator measuring wether an app is paid or free, all apps that are free will be correlated with apps that have a price = 0 and apps that are paid will be correlated with apps that have a price greater than 0. 

```{r int-type}
ggplot(apps, aes(x = Type, y = Rating, color = Price)) + geom_point() +
labs( title = "Relationship between Tyle and Rating", x ="Type", y = "Rating out of 5")
```

This is further illustrated through the above plot, which clearly shows this interaction. These interactions along with any further ones we may find after our preliminary analysis will have to be explored further and considered when building our model. 

## Section 4. References

## The Data
```{r glimpse}
glimpse(apps)
```